---
title: "Finding files"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if("librarian" %in% installed.packages()==FALSE){
  install.packages("librarian")
}
library(librarian)
shelf(knitr, here, quiet = TRUE)
```

# Load data by specifying the path to the file
Can you run the following code chunk? On its own? When knitting the whole Rmd file?
```{r direct-path}
dat <- read.csv("data/languages.csv") 
kable(head(dat), caption = "Specifying path directly")
```

# The here package
The `here` command (part of the `here` package) prints the path to what it thinks is a sensible "root" location for the current file or project. This may or may not be the same as the current *working directory* -- the place where R will look by default when importing files, saving files and so on.
```{r}
getwd() # The path to the current working directory
here() # The path to a sensible place to look for files
```


```{r using-here}
dat <- read.csv(here("data", "languages.csv"))
kable(tail(dat), caption = "Using here() to specify path")
```
